Refinement for open automata

### 2021-05-01 2021-Refinement/report.tex
Fixed double bracket

Let's look at the \(\tau\) transition from the state \(R\) for a more in depth example on how composition and value passing work.
The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{R \mapsto \act{set}\mpar{x}, C \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
The composition makes 12 states from the \(R\) state, these states are in \(\mbrc{R} \times \mbrk{1; 6} \times \mbrc{S, C}\), however only \(\mpar{R, 1, S}\) and \(\mpar{R, 2, C}\) are reachable so we will only consider these two.
In the figure they are noted \(RS\) and \(RC\).
The holes \(R\) and \(C\) are filles at the same time so the \(\tau\) transition must synchronise with a transition from both the register and the controller.

>>>>

Let's look at the \(\tau\) transition from the state \(R\) for a more in depth example on how composition and value passing work.
The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{R \mapsto \act{set}\mpar{x}, C \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
The composition makes 12 states from the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(\mpar{R, 1, S}\) and \(\mpar{R, 2, C}\) are reachable so we will only consider these two.
In the figure they are noted \(RS\) and \(RC\).
The holes \(R\) and \(C\) are filles at the same time so the \(\tau\) transition must synchronise with a transition from both the register and the controller.
